---
title: "Joins"
author: "Grace Lewin"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(lubridate)
```

## Warm Up: data wrangling

```{r}
ex_1 <- penguins %>% 
  filter(island %in% c("Biscoe", "Dream")) %>% 
  select(-year, -sex) %>% # could also do select(-c(year, sex))
  mutate(body_mass_kg = body_mass_g/1000) %>% 
  rename(location = island) # new name = old name
```


```{r}
ex_2 <- penguins %>% 
  filter(species == "Adelie") %>% 
  filter(!is.na(flipper_length_mm)) %>% # could also do drop_na(flipper_length_mm)
  group_by(sex) %>% 
  summarize(
    mean_flip <- mean(flipper_length_mm),
    sd_flip <- sd(flipper_length_mm),
    sample_size = n()
  )

ex_2
```


## Joins practice

## Mutating Joins

```{r}
animals <- tibble::tribble(
  ~location,   ~species,  ~maturity,
   "lagoon",   "bobcat",    "adult",
    "bluff",   "coyote", "juvenile",
    "creek",      "fox",    "adult",
     "oaks", "squirrel", "juvenile",
    "bluff",   "bobcat",    "adult"
  )

sites <- tibble::tribble(
  ~location,      ~full_site_name, ~jurisdiction,
    "beach",       "Goleta Beach",     "SB City",
   "lagoon",        "UCSB Lagoon",        "UCSB",
    "bluff",       "Ellwood Mesa",     "SB City",
     "oaks", "Fremont Campground",        "USFS"
  )
```


### Full Join

everything from both data frames is returned, regardless of whether or not it has a match in the data frame it's being joined to.

```{r}
animals_full_join <- full_join(animals, sites)
```

### Left Join

everything in x is kept. Things in y that have a matching key in x are joined to it. Things in y that do not have a matching key are dropped.

```{r}
animals_left_join <- left_join(animals, sites)
```

### Inner Join

only keeps stuff if they have a key match in x and y.

```{r}
animals_inner_join <- inner_join(animals, sites)
```

## Filtering Joins

### Semi join

```{r}
animals_semi_join <- semi_join(animals, sites, by = "location")
```

## Anti join

```{r}
animals_anti_join <- anti_join(sites, animals, by = "location")
```


